An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/intro.tex
config: intro

The downside of these approaches is that their learning approaches 
are limited to simplistic configuration errors, 
such as type errors and syntax errors, or they 
heavily rely on template-based inference~\cite{zhang14encore}. 
%As we mentioned earlier, 
%because configuration files are not written in a typed language 
%with a fixed syntax,
%type errors and syntax errors are relatively rare and easy to detect. 
Many sophisticated configuration errors, 
which are difficult to template in practice, 
cannot be detected by this way. 
As an illustration of such an error, consider the ordering errors, 
which happens when some entries are inserted in a wrong order. 
For example, if in a PHP configuration file 
an entry {\tt extension = mysql.so} appears 
before {\tt extension = recode.so},  
it would lead to a crash error, where the Apache server cannot start 
due to the segmentation fault error. The correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical}.
These types of errors cannot be detected by existing
learning efforts, 
since it is hard to build a corresponding template~\cite{xu15systems}. 
%we would need to capture ordering relations of all the entries. 
%Some of them can appear in an arbitrary ordering, 
%and the resulting templates would be too large 
%and not efficient for a practical use.

@@

For practical purposes we use the dataset given at~\cite{configdataset}. 
Every file in our dataset contains several errors, 
but they are typically different errors and only appear 
in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
accurate set of rules. The rules, in general, specify which properties do variables need to satisfy. One can see this learning process as a
way of deriving  
a specification for configuration files.  Once there is a specification, we can do a formal verification. With these 
rules we can efficiently check the correctness of the configuration files
of interest and detect potential errors.

The learning process works in two phases. In the first phase, 
\app analyzes the sample dataset and generates a 
well-structured and probabilistically-typed 
intermediate representation. 
In the second phase, \app derives rules and constraints by analyzing
the intermediate representations.  Every learned rule is annotated with a probability depicting in
which percentage of the files the rule was seen as correct. We only accept those rules whose 
correctness probability is above the given threshold.

@@

\item We propose the first automatic configuration verification
framework, \app, that can learn a language model from an example set of 
correct configuration files, and then use this language model to verify 
configuration files of interest.

>>>>

The downside of these approaches is that their learning approaches 
are limited to simplistic configuration errors, 
such as type errors and syntax errors, or they 
heavily rely on template-based inference~\cite{zhang14encore}. 
%As we mentioned earlier, 
%because configuration files are not written in a typed language 
%with a fixed syntax,
%type errors and syntax errors are relatively rare and easy to detect. 
Many sophisticated configuration errors, 
which are difficult to template in practice, 
cannot be detected by this way. 
As an illustration of such an error, consider the entry ordering errors, 
which happens when some entries are inserted in a wrong order. 
For example, if in a PHP configuration file 
an entry {\tt extension = mysql.so} appears 
before {\tt extension = recode.so},  
it would lead to a crash error, where the Apache server cannot start 
due to the segmentation fault error. The correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical}.
These types of errors cannot be detected by existing
learning efforts, 
since it is hard to build a corresponding template~\cite{xu15systems}. 
%we would need to capture ordering relations of all the entries. 
%Some of them can appear in an arbitrary ordering, 
%and the resulting templates would be too large 
%and not efficient for a practical use.

@@

For practical purposes we use a real-world dataset~\cite{configdataset}. 
Every file in our dataset contains several errors, 
but they are typically different errors and only appear 
in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
accurate set of rules. The rules, in general, specify which properties do variables need to satisfy. One can see this learning process as a
way of deriving  
a specification for configuration files.  Once there is a specification, we can do a formal verification. With these 
rules we can efficiently check the correctness of the configuration files
of interest and detect potential errors.

The learning process has two phases. In the first phase, 
\app analyzes the sample dataset and generates a 
well-structured and probabilistically-typed 
intermediate representation. 
In the second phase, \app derives rules and constraints by analyzing
the intermediate representations.  Every learned rule is annotated with a probability depicting in
which percentage of the files the rule was seen as correct. We only accept those rules whose 
correctness probability is above the given threshold.

@@

\item We propose the first automatic configuration verification
framework, \app, that can learn a language model from a sample
dataset, and then use this language model to verify 
configuration files of interest.
